A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-14 application_to_path_tracing.tex
Small change
presque 12 pages
Essai

with $\alpha$ the angle between $\overrightarrow{ximp_n}$ and $\Phi$, $s$ being a parameter called skeleton strength. The higher $s$ is, the more we sample close $\overrightarrow{ximp_n}$.

@@

We present some results of our algorithm applied to four scenes. The first row shows our result and the second row shows a standard path tracing with the same input parameters. On each picture a MSE (mean square error) value with a reference image is shown.

\begin{figure}[htp]
\begin{center}
\includegraphics[scale=0.17]{images/four_scenes_for_dgci.png}
\caption{Four images comparing the classic path tracing (image $a$ and $c$) and our method (image $b$ and $d$). Note the noise reduction of our method in the left wall of images $a$ and $b$, and on the floor on image $c$ and $d$.}
\end{center}
\end{figure}

We observe that images produced by our algorithm have less noise than the ones produced by the regular path tracing (for a same number of rays shot per pixel). The MSE values are lower for the top pictures, meaning that we converge faster to the reference image than standard path tracing does.

This image is a zoom that allows us to see more precisely the the reduction of noise for our method.

>>>>

with $\alpha$ the angle between $\overrightarrow{ximp_n}$ and $\Phi$, $s$ being a parameter called skeleton strength. The higher $s$ is, the more we sample close $\overrightarrow{ximp_n}$.
\begin{figure}[thp]
\begin{center}
\includegraphics[scale=0.17]{images/four_scenes_for_dgci.png}
\caption{\label{fig:results}Four images comparing the classic path tracing (image $a$ and $c$) and our method (image $b$ and $d$). Note the noise reduction of our method in the left wall of images $a$ and $b$, and on the floor on image $c$ and $d$.}
\end{center}
\end{figure}

@@
